Estimating individual subjective values of emotion regulation strategies

### 2022-06-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex

How do people choose strategies from their repertoire?
Similarly to the expectancy-value model of emotion regulation\textsuperscript{18} it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice\textsuperscript{19}) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs\textsuperscript{20}.
For example, a study found that the intensity of a stimulus or situation plays a role in the choice\textsuperscript{21}.
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction\textsuperscript{20,21}.
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort\textsuperscript{20,22}.
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy\textsuperscript{22}.
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
Furthermore, the research on ER choice lacks information regarding the strategies that were \emph{not} chosen in each case.
It is unclear whether people had clear preferences or whether the choice options were similarly attractive.

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement\textsuperscript{12}.
One certainly central goal is the regulation of negative affect.
A second, intrinsic and less obvious goal is the avoidance of effort\textsuperscript{23}.
When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24} and chose strategies that were less effortful\textsuperscript{22}.
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
In addition, perceived utility should have an impact on SVs.
A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
Moreover, SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for only one strategy or low SVs for all of the strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.

So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)\textsuperscript{25}.

In the original study by Westbrook et al.\textsuperscript{25}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies\textsuperscript{22}.
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{25} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{26}).

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{27}.
The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{28}.
We used \emph{R} with \emph{R Studio}\textsuperscript{29,30} with the main packages \emph{afex}\textsuperscript{31} and \emph{BayesFactor}\textsuperscript{32} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{33} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
The second session will take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
After that, participants will choose one ER strategy to repeat one more time.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{34,35}.

@@

The online survey will contain a number of questionnaires.
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{36}.\\
It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
The items are rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.

Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{37,38}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{41} will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,42}.
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{43}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{44,45} will be used.
To assess self-control,\textsuperscript{46} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{47}, the Brief Self-Control Scale (BSCS)\textsuperscript{48,49}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{50,51}.
Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{52}.
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{25} with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies will be presented with a monetary reward.
The order of the pairings will be randomized.
Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
The participants decide by clicking the on-screen button of the respective option.
The strategy that is not chosen will be assigned the fixed value of 2 €, the chosen strategy will be assigned a starting value of 1 €.
From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{25}.
Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.

@@

Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{53} and the International Affective Picture System (IAPS)\textsuperscript{54}.
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
An evolutionary algorithm\textsuperscript{55} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material 1.
The five sets of negative pictures will be assigned randomly to the blocks.

@@

Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{56}, similar to previous work by our group\textsuperscript{7}.
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{57}
The ground electrode will be placed over the left \emph{Mastoid}.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 \(k\Omega\).
Data will be sampled at 1000 Hz, filtered, rectified and integrated.
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{56}
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.

@@

Sample size calculation is done using \emph{G*Power}\textsuperscript{58,59}.
In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of at least \(N=85\) have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of \(N=120\) participants, about \(50%
\) more data sets, than necessary.
Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.

@@

To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG \emph{corrugator} and \emph{levator} activity.
Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
rmANOVAS will be run using the \emph{afex} package\textsuperscript{31}.

@@

To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
rmANOVAS will be run using the \emph{afex} package\textsuperscript{31}.

@@

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{60}.
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
\[
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
\]
Level-1-predictors will be centered within cluster\textsuperscript{61}.
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).

@@

For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{32}, will be reported.
Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.

@@

\leavevmode\hypertarget{ref-Westbrook2013}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Westbrook, A., Kester, D. \& Braver, T. S. What is the subjective cost of cognitive effort? {Load}, trait, and aging effects revealed by economic preference. \emph{PLOS ONE} \textbf{8}, e68210 (2013).}

\leavevmode\hypertarget{ref-Zerna2022}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Zerna, J., Scheffel, C., Kührt, C. \& Strobel, A. When easy is not preferred: An effort discounting for estimating subjective values of taks. \emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}

>>>>

How do people choose strategies from their repertoire?
Similarly to the expectancy-value model of emotion regulation\textsuperscript{18} it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice\textsuperscript{19}) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs\textsuperscript{20}.
For example, a study found that the intensity of a stimulus or situation plays a role in the choice\textsuperscript{21}.
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction\textsuperscript{20,21}.
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort\textsuperscript{20,22}.
Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
Furthermore, the research on ER choice lacks information regarding the strategies that were \emph{not} chosen in each case.
It is unclear whether people had clear preferences or whether the choice options were similarly attractive.

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement\textsuperscript{12}.
One certainly central goal is the regulation of negative affect.
The effectiveness of ER strategies should therefore influence the respective SV.
A second, intrinsic, and less obvious goal is the avoidance of effort\textsuperscript{23}.
When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24}.
Cognitive effort avoidance has been reported in many contexts, for example in affective context\textsuperscript{25}, the context of decision making\textsuperscript{26}, and executive functions\textsuperscript{27}, and is associated with Need for Cognition (NFC)\textsuperscript{28}, a stable measure of the individual pursuit and enjoyment of cognitive effort\textsuperscript{29,30}.
In the area of emotion regulation, too, there are initial indications that people show a tendency towards effort avoidance.
Across two studies, we could show in previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy\textsuperscript{22}.
In our studies, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Moreover, the majority of participants stated afterwards the main reason for their choice was effort.
We assume therefore that, although individuals trade off both factors - effectiveness and effort - against each other, effort should be the more important predictor for SVs of ER strategies.
In addition, perceived utility should have an impact on SVs.
A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for one strategy or low SVs for all of the strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.

So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)\textsuperscript{29}.

In the original study by Westbrook et al.\textsuperscript{29}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies\textsuperscript{22}.
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{29} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{31}).

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{32}.
The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{33}.
We used \emph{R} with \emph{R Studio}\textsuperscript{34,35} with the main packages \emph{afex}\textsuperscript{36} and \emph{BayesFactor}\textsuperscript{37} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{38} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
The second session will take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
After that, participants will choose one ER strategy to repeat one more time.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{39,40}.

@@

The online survey will contain a number of questionnaires.
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{41}.\\
It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
The items are rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.

Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{42,43}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{46} will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,47}.
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{48}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,49} will be used.
To assess self-control,\textsuperscript{50} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{51}, the Brief Self-Control Scale (BSCS)\textsuperscript{52,53}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{54,55}.
Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{56}.
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{29} with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies will be presented with a monetary reward.
The order of the pairings will be randomized.
Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
The participants decide by clicking the on-screen button of the respective option.
The strategy that is not chosen will be assigned the fixed value of 2 €, the chosen strategy will be assigned a starting value of 1 €.
From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{29}.
Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.

@@

Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{57} and the International Affective Picture System (IAPS)\textsuperscript{58}.
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
An evolutionary algorithm\textsuperscript{59} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material 1.
The five sets of negative pictures will be assigned randomly to the blocks.

@@

Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{60}, similar to previous work by our group\textsuperscript{7}.
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{61}
The ground electrode will be placed over the left \emph{Mastoid}.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 \(k\Omega\).
Data will be sampled at 1000 Hz, filtered, rectified and integrated.
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{60}
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.

@@

Sample size calculation is done using \emph{G*Power}\textsuperscript{62,63}.
In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of at least \(N=85\) have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of \(N=120\) participants, about \(50%
\) more data sets, than necessary.
Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.

@@

To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG \emph{corrugator} and \emph{levator} activity.
Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
rmANOVAS will be run using the \emph{afex} package\textsuperscript{36}.

@@

To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
rmANOVAS will be run using the \emph{afex} package\textsuperscript{36}.

@@

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{64}.
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
\[
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
\]
Level-1-predictors will be centered within cluster\textsuperscript{65}.
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).

@@

For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{37}, will be reported.
Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.

@@

\leavevmode\hypertarget{ref-Gonzalez-Garcia2021}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Gonzalez-Garcia, C. \emph{et al.} Induced affective states do not modulate effort avoidance. \emph{Psychol Res} \textbf{85}, 1016--1028 (2021).}

\leavevmode\hypertarget{ref-Kool2010}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Kool, W., McGuire, J. T., Rosen, Z. B. \& Botvinick, M. M. Decision making and the avoidance of cognitive demand. \emph{J Exp Psychol Gen} \textbf{139}, 665--82 (2010).}

\leavevmode\hypertarget{ref-Cheval2020}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Cheval, B. \emph{et al.} Higher inhibitory control is required to escape the innate attraction to effort minimization. \emph{Psychology of Sport and Exercise} \textbf{51}, (2020).}

\leavevmode\hypertarget{ref-Cacioppo1982}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
